Robust Adaptation to Multi-Scale Climate Variability

### 2018-10-30 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
update the key points because only 3 are allowed
put together a poster for the NEXUS conference

% Key Points
\begin{keypoints}
  \item Climate risk varies in time over a project's finite planning period
  \item The dominant driver of climate risk depends on the length of the planning period 
  \item Potentially predictable cyclical climate variability dominates near-term climate risk
  \item Successful climate adaptation requires prediction of short- and long-term climate variability over the planning period
\end{keypoints}

@@

As described in \cref{sec:methods-generating}, we use a synthetic NINO3 time series, as described in \citep{Ramesh:2016hf}, to represent low-frequency climate variability.
\Cref{fig:enso-ts} shows the wavelet spectrum of this time serties, calculated using WaveletComp software \citep{Roesch:wlBQQoIs}.
The global (average) wavelet power spectrum shows a clear peak around 3-7 years, in line with previous studies of \gls{enso} although interactions with other modes of \acrfull{lfv} found in some studies \citep{Jin:1994wq} is dampened in this model.
There are, however, modes of \gls{lfv} between \SIrange{16}{128}{year} which are \emph{locally} strong at some points in time, which captures at least some effects of very low-frequency behavior for the purposes of this study.
\begin{figure}
  \includegraphics[width=\textwidth]{enso_wavelet.png}
  \caption{
    Wavelet analysis of the synthetic annual NINO3 time series described in \cref{sec:methods-generating}.
    (L): wavelet power spectrum.
    (R): global (average) power spectrum.
    Blue dots indicate frequencies which are significant at $\alpha=0.10$ and red dots frequencies which are significant at $\alpha=0.05$ compared to white noise.
  }\label{fig:enso-ts}
\end{figure}

>>>>

% Key Points
\begin{keypoints}
  \item Climate risk varies in time over a project's finite planning period
  \item Cyclical climate variability (anthropogenic climate change) dominates near-term (long-term) climate risk
  \item Successful climate adaptation requires prediction of short- and long-term climate variability over the planning period
\end{keypoints}

@@

As described in \cref{sec:methods-generating}, we use a synthetic NINO3 time series, as described in \citep{Ramesh:2016hf}, to represent low-frequency climate variability.
\Cref{fig:enso-ts} shows the wavelet spectrum of this time series, calculated using WaveletComp software \citep{Roesch:wlBQQoIs}.
The global (average) wavelet power spectrum shows a clear peak around 3-7 years, in line with previous studies of \gls{enso} although interactions with other modes of \acrfull{lfv} found in some studies \citep{Jin:1994wq} is dampened in this model.
There are, however, modes of \gls{lfv} between \SIrange{16}{128}{year} which are \emph{locally} strong at some points in time, which captures at least some effects of very low-frequency behavior for the purposes of this study.
\begin{figure}
  \includegraphics[width=\textwidth]{enso_wavelet.png}
  \caption{
    Wavelet analysis of the synthetic annual NINO3 time series described in \cref{sec:methods-generating}.
    (L): wavelet power spectrum.
    (R): global (average) power spectrum.
    Blue dots indicate frequencies which are significant at $\alpha=0.10$ and red dots frequencies which are significant at $\alpha=0.05$ compared to white noise.
  }\label{fig:enso-ts}
\end{figure}
